\documentclass[10pt,a4paper]{book}

\usepackage[english]{babel}
\usepackage{graphicx}

\usepackage{algorithm}
\usepackage{algpseudocode}

%Import the natbib package and sets a bibliography  and citation styles
\usepackage{natbib}
\bibliographystyle{abbrvnat}
\setcitestyle{authoryear,open={(},close={)}}

% ****** Margings ******
\textwidth = 6.5 in
\textheight = 9 in
\topmargin = -0.5 in
\evensidemargin = 0 in
\oddsidemargin = 0 in
\parskip = 0.1 in
\parindent = 0 in
\tabcolsep = 5 pt

% ******* HEADERS ******
\author{Jorge E. Mendoza}
\title{HDR}

\begin{document}

% *********** TITTLE ***************
\maketitle

% *********** CONTENTS ***************
\tableofcontents


% *********** INTRODUCTION ***************
\chapter{Introduction}

% *********** TECHNICAL ***************
\input{./tex/technical_background.tex}


% *********** STOCHASTIC ***************
\input{./tex/stochastic.tex}

% *********** BIBLIOGRAPHY ***************
\bibliography{mybib}

% *********** END ***************
%\end{document}


% *********** ELECTRIC ***************
\chapter{Electric vehicle routing}
  \section{Battery charging policies and charging function approximations}  
  	\subsection{Full charging with constant charging times}
  	Paper: Montoya et al.(2016a)
  	\subsection{Partial charging with non-linear charging times}
  	Paper: Montoya et al. (2016b)
  \section{Charging station capacity}
    Working paper: Froger et al. (2017)
  \section{Uncertain charging station availability}
  	Working paper: Kullman, Goodson, and Mendoza (2017)
  \section{Shared charging infrastructure}
  	Working paper: Kok et al. (2017)
  \section{Perspectives}
  \subsection{Considering battery degradation costs}
  	On going Ph.D. Thesis: Laura Echeverri
  \subsection{Multigraph formulations: trading off energy consumption and travel time}
  	Future Post-doctoral project: Cagri Kok
  \subsection{Uncertain energy consumption}
  	Future Ph.D. internship: Samuel Pelletier

% *********** APPLICATIONS ***************
\chapter{Industrial applications}
  \section{Vehicle routing in a public utility}
  Paper: Mendoza, Medaglia, and Velasco (2009)
  \section{Technician routing with electric and conventional vehicles}
  Working paper: Montoya et al. (2017)
  \section{Maintenance scheduling in the wind industry}
  Paper: Froger et al. (2016a)\\
  Working papers: Froger et al. (2016b, 2016c)
  \section{The pre-pack optimization problem}
  Book chapter: Hoskins et al. (2014)
% *********** VRP-REP ***************
\chapter{VRP-REP: the vehicle routing problem repository}
Working paper: Mendoza et al. (2017)

% *********** CONCLUSIONS ***************
\chapter{Conclusions and perspectives}

\begin{appendix}
\chapter{Curriculum Vitae}
\chapter{Selected journal articles}
\end{appendix}
\end{document}